### 2017-01-30 presentation/parrows.tex
wip on presentation

\section{Parallel Arrows}
\subsection{The ArrowParallel typeclass}
\begin{lstlisting}[frame=htrbl]
parEvalN :: [a -> b] -> [a] -> [b]
\end{lstlisting}

@@

\frbreak

@@

\frbreak

\subsection{Multicore Haskell}
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = listApp fs >>> arr (flip using $ parList rdeepseq)
\end{lstlisting}

\frbreak
\subsection{ParMonad}
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = 
			(arr $ \as -> (fs, as)) >>>
			zipWithArr (app >>> arr spawnP) >>>
			arr sequenceA >>>
			arr (>>= mapM get) >>>
			arr runPar
\end{lstlisting}

\frbreak
\subsection{Eden}
\begin{lstlisting}[frame=htrbl]
instance (Trans a, Trans b) => ArrowParallel (->) a b conf where
parEvalN _ fs as = spawnF fs as
\end{lstlisting}
and the Kleisli type.
\begin{lstlisting}[frame=htrbl]
instance (Monad m, Trans a, Trans b, Trans (m b)) =>
	ArrowParallel (Kleisli m) a b conf where
parEvalN conf fs =
	(arr $ parEvalN conf (map (\(Kleisli f) -> f) fs)) >>>
	(Kleisli $ sequence)
\end{lstlisting}

\begin{lstlisting}[frame=htrbl]
class (Arrow arr) => ArrowUnwrap arr where
arr a b -> (a -> b)
\end{lstlisting}

\frbreak

\subsection{Benefits of parallel Arrows}

>>>>

\subsection{Generalization to Arrows}

\begin{frame}[fragile]{The ArrowParallel typeclass}
\begin{lstlisting}[frame=htrbl]
parEvalN :: [a -> b] -> [a] -> [b]
\end{lstlisting}

@@

@@

\end{frame}

### 2017-01-30 presentation/utilityFunctions.tex
wip on presentation

\section{Utility Functions}\label{utilfns}
\subsection{mapArr}
The mapArr combinator lifts any arrow \code{arr a b} to an arrow \code{arr [a] [b]} \cite{programming_with_arrows},
\begin{lstlisting}[frame=htrbl]
mapArr :: ArrowChoice arr => arr a b -> arr [a] [b]
mapArr f =
	arr listcase >>>
	arr (const []) ||| (f *** mapArr f >>> arr (uncurry (:)))
	where
		listcase [] = Left ()
		listcase (x:xs) = Right (x,xs)
\end{lstlisting}
with
\begin{lstlisting}[frame=htrbl]
(|||) :: ArrowChoice arr a c -> arr b c -> arr (Either a b) c
\end{lstlisting}
%It takes two arrows \code{arr a c} and \code{arr b c} and combines them into a new arrow \code{arr (Either a b) c} which pipes all \code{Left a}'s to the first arrow and all \code{Right b}'s to the second arrow.
\frbreak

\subsection{zipWithArr \& listApp}
zipWithArr lifts any arrow \code{arr (a, b) c} to an arrow \code{arr ([a], [b]) [c]}:
\begin{lstlisting}[frame=htrbl]
zipWithArr :: ArrowChoice arr => arr (a, b) c -> arr ([a], [b]) [c]
zipWithArr f = (arr $ \(as, bs) -> zipWith (,) as bs) >>>
	mapArr f
\end{lstlisting}
listApp converts a list of arrows \code{[arr a b]} to a new arrow \code{arr [a] [b]}:
\begin{lstlisting}[frame=htrbl]
listApp :: (ArrowChoice arr, ArrowApply arr) =>
	[arr a b] -> arr [a] [b]
listApp fs = (arr $ \as -> (fs, as)) >>> zipWithArr app
\end{lstlisting}
with the \code{ArrowApply} that defines \code{app :: arr (arr a b, a) c}.

>>>>

\subsection{Utility Functions}\label{utilfns}
\begin{frame}[fragile]{mapArr}
The mapArr combinator lifts any arrow \code{arr a b} to an arrow \code{arr [a] [b]} \cite{programming_with_arrows},
\begin{lstlisting}[frame=htrbl]
mapArr :: ArrowChoice arr => arr a b -> arr [a] [b]
mapArr f =
	arr listcase >>>
	arr (const []) ||| (f *** mapArr f >>> arr (uncurry (:)))
	where
		listcase [] = Left ()
		listcase (x:xs) = Right (x,xs)
\end{lstlisting}
with
\begin{lstlisting}[frame=htrbl]
(|||) :: ArrowChoice arr a c -> arr b c -> arr (Either a b) c
\end{lstlisting}
%It takes two arrows \code{arr a c} and \code{arr b c} and combines them into a new arrow \code{arr (Either a b) c} which pipes all \code{Left a}'s to the first arrow and all \code{Right b}'s to the second arrow.
\end{frame}

\begin{frame}[fragile]{zipWithArr \& listApp}
zipWithArr lifts any arrow \code{arr (a, b) c} to an arrow \code{arr ([a], [b]) [c]}:
\begin{lstlisting}[frame=htrbl]
zipWithArr :: ArrowChoice arr => arr (a, b) c -> arr ([a], [b]) [c]
zipWithArr f = (arr $ \(as, bs) -> zipWith (,) as bs) >>>
	mapArr f
\end{lstlisting}
listApp converts a list of arrows \code{[arr a b]} to a new arrow \code{arr [a] [b]}:
\begin{lstlisting}[frame=htrbl]
listApp :: (ArrowChoice arr, ArrowApply arr) =>
	[arr a b] -> arr [a] [b]
listApp fs = (arr $ \as -> (fs, as)) >>> zipWithArr app
\end{lstlisting}
with the \code{ArrowApply} that defines \code{app :: arr (arr a b, a) c}.
\end{frame}
